Put Title here

### 2018-11-23 General WLD combinatorics.tex

\begin{lem}\label{lem facts about WLD matroids}
Let $W = (\cP,n)$ be an admissible Wilson loop diagram. Then:
\begin{enumerate}
\item The rank of a set $V \subseteq [n]$ is bounded above by $\min\{|V|,|\Prop(V)|\}$, with $\rk(V) = |V|$ if and only if $V$ is an independent set.
%\item Let $v \in [n]$ and $q \in \Prop(v)$. Then for any $V \subset [n]$ such that $q \not \in \Prop(V)$, we have $\rk(V \cup \{v\}) = \rk(V) +1$, i.e. adding a vertex that supports a new propagator to a set increases the rank of the set.
\item If $C \subseteq [n]$ is a cycle, then $\rk(C) = |Prop(C)|$.
\end{enumerate}
\end{lem}
\begin{proof}
The first part of (1) is \cite[Equation (9)]{wilsonloop} and surrounding discussion, and the second part is standard matroid theory. (2) is \cite[Lemma 3.27]{wilsonloop}.
\end{proof}

@@

\begin{lem} \label{lem decompose flat}Let $F$ be a flat in $M(W)$, and let $C \subseteq F$ be the union of all circuits contained in $F$. Then the following are true:
\begin{enumerate}
\item $C = F(\Prop (C))$, i.e. $C$ is a propagator flat.
\item $F \setminus C$ is an independent \st{set. Further, if $W$ does not contain any vertices of rank $0$, i.e. all vertices support at least $1$ propagator, then $F \setminus C$ is an independent} flat. \sanote{$F$ and $C$ both contain all vertices of rank $0$ by definition} 
\end{enumerate}
\end{lem}

@@

Let $v \in C$. Clearly $\Prop(v) \subseteq \Prop(C)$, and so by Lemma \ref{lem properties of prop flats} we have $F(\Prop(v)) \subseteq F(\Prop(C))$. Since $v \in F(\Prop(v))$ by the definition of propagator flat, we have $v \in F(\Prop(C))$ as required.

@@

For part (2), first note that $F \setminus C$ is automatically independent as it contains no circuits. Now suppose that all vertices in $W$ have rank $\geq 1$. \sanote{can get rid of?}

@@

\begin{lem} \label{maxexactcomplementrank}
Let $W = (\cP, n)$ be a Wilson loop diagram, and $P \subsetneq \cP$. Then: \note{should hold if $P = \cP$.}
\begin{enumerate}
\item If $(P,V(P))$ is an exact subdiagram in $W$, then $\rk(F(P^c)) = |P^c|$.
\item If $(P,V(P))$ is a maximal exact subdiagram in $W$, then $F(P^c)$ is a cyclic flat.
\end{enumerate}
\end{lem}

{\color{violet} Note that by definition, since $F(P^c)$ has at $|P^c|$ propagators in it, this is an upper bound on the rank. However, showing equality on the first part is harder.}

@@

We address part (2) first. Suppose that $(P, V(P))$ is a maximal exact subdiagram; by Corollary \ref{classifyflats} we can decompose $F(P^c)$ as
\begin{equation}\label{eq decompose F}F(P^c) = C \sqcup S,\end{equation}
where $C$ is the largest cyclic flat contained in $F(P^c)$ and $S$ is an  independent set. Note that $C$ must be non-empty since $F(P^c)$ is dependent. {\color{violet}We proceed by showing that $S$ must be empty, forcing $F(P^c)$ to be a cyclic flat.} \sanote{Does this fix confusion later?}

Since $C = F(\Prop(C))$ by Lemma \ref{lem decompose flat}, define $Q := \Prop(C)^c$ so that we may write $C = F(Q^c) = V(Q)^c$. {\color{violet}Note that since $C \subseteq F(P^c)$, $P \subseteq Q$. }Furthermore, we have 
\begin{equation}\rk(S) = |S| \leq \rk(F(P^c)) - \rk(C)  \leq |P^c| - \rk(C) \;, \label{increasingrank}\end{equation}
where first equality comes from the fact that $S$ is an independent set, and the final inequality comes from Lemma \ref{lem facts about WLD matroids}(1). Since $\rk(C) = |\Prop(C)| = |Q^c|$ by Lemma \ref{lem facts about WLD matroids}(2), we can rearrange \eqref{increasingrank} to obtain the inequality
\begin{equation} |P| + |S| \leq |P| + |P^c| - \rk(C) = |Q| \;. \label{Qsizebound}\end{equation}
Furthermore, since $V(Q) = S \sqcup V(P)$ (by equation [ref] and the definition of $Q$) we may write  
\begin{equation} |V(Q)| = |S| + |V(P)| = |S| + |P| +3 \label{VQsize} \;.\end{equation} 
Combining this with \eqref{Qsizebound} gives $|V(Q)| - 3 \leq |Q|$. That is, either $W$ was not admissible, \hlfix{or $(P,V(P))$ was not a maximal exact subdiagram.}{This only follows if $P \subseteq Q$, which I can't see? We don't ever seem to use the fact that $S$ is empty/nonempty} In other words, $S$ cannot be non-empty, proving that $F(P^c)$ is a cyclic flat, and therefore of maximal rank.

{\color{violet}REPLACE BELOW WITH: Let $P$ be a maximal exact subdiagram as above, and let $(R, V(R))$ be an exact subdiagram that is not maximal. That is, $R \subsetneq P$. }

Let $(Q, V(Q))$ be an exact subdiagram that is not maximal, with \hlfix{$Q \subset P$ defining the maximal exact subdiagram above}{If I've understood this right, we would need to show that any exact subdiagram appears as $\Prop(C)^c$ for some maximal exact $P$ first} . \sanote{why? I don't understand your confusion}

{\color{violet}POSSIBLY REPLACE BELOW WITH: Since $R \subset P$, $V(P) = V(R) \sqcup S$. Since $P$ and $R$ both define exact subdiagrams, we may write $|V(P)| = |V(R)| + |P \setminus R|$, where $S$ is a vertex set of size $|P \setminus R|$ with $(P \setminus R \subset \Prop(S)$. Since $\rk V(P) =  \rk V(R) + |P \setminus R|$, $S$ is independent. Taking the complements, we may write \bas F(R^c ) = F(P^c) \sqcup S \;.\eas Since $S$ is an independent set of vertices of the correct size supporting the appropriate propagators, this gives $ \rk F(R^c ) = |R^c|$.}

Using the fact that $P$ and $Q$ are both exact diagrams, we have $|V(P)| = |V(Q)| + |P \setminus Q|$.  Then $V(Q)^c = F(P^c) \cup S$, where $S$ is an independent set of size $|P \setminus Q|$ and with $(P \setminus Q) \subset \Prop (S)$. Therefore, \hlfix{$\rk (F(Q^c)) = |Q^c|$.}{I'm lost here.} \sanote{better if I fix typo?}
\end{proof}

@@

In \cite{wilsonloops}, the authors show that all exact Wilson loop diagrams correspond to positroids. That is, they correspond to matroids that can be represented by elements of the positive Grassmannians $\Gr(|\cP|, |V|)$.\todo{Check: positroids or totally positive? Why specify exactness?}

\begin{dfn}
Given a Wilson loop diagram $W$, define the positroid cell associated to a Wilson loop diagram, $\Sigma(W)$, to be the cell in the CW complex on $\Gr(|\cP|, |V|)$ defined by the \hlfix{realizations}{we haven't specified what this means}  of $W$ that lie in $\Gr(|\cP|, |V|)$.
\end{dfn}

@@

%\note{I don't think rank of a vertex (in the sense of number of propagators supported on it) was ever used, so I removed the definition}
%\note{rank probably isn't a good word; do we have a better one?}
%\begin{dfn}\label{vertex rank}
%Let $i$ be a vertex in $W$. We define the {\bf rank} of $i$ to be $|Prop(i)|$, i.e. the number of propagators supported on $i$.
%\end{dfn}

@@

\begin{dfn}\note{right now this doesn't depend on the order of $i$ and $j$, but that might matter later on?}
Let $p$ be a propagator supported on $(i,j)$.  Define the \textit{length} of $p$ to be 
\[\ell(p) = min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
\end{dfn}

\begin{rmk}\label{rem:props of length 2 and 3}
The following observations about propagators of short length in $W$ are easily verified:
\begin{itemize}
\item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.
\item If $p = (i,i+3)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
\end{itemize}
\end{rmk}

@@

\begin{lem}\label{lem sian 1}
  Let $W$ be an admissible WLD in which each vertex supports at least one propagator.  Then exactly one of the following two things occurs.
  \begin{enumerate}
    \item $W$ has a propagator of length 3 with a propagator of length 2 inside it.
    \item $W$ admits no propagators of length 3, and one or more of the following things occurs.
      \begin{enumerate}
        \item There is a propagator of length $2$, say $(i, i+2)$ such that no other propagators ends on either the edge $i$ or the edge $i+2)$.\label{item lonely 2}
        \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
        \item There exists a propagator of length 4 with only a propagator of length 2 inside it.\label{item 4 and 2}
      \end{enumerate}
  \end{enumerate}
\end{lem}

\begin{proof}
  Suppose first that $W$ has a propagator of length $3$, $p=(i, i+3)$.  By Remark~\ref{rem:props of length 2 and 3} along with the fact that every vertex of $W$ supports at least one propagator, we have that $i+2$ supports exactly one propagator and this propagator must have length 2 by noncrossingness.

@@

We need a bit of notation:
Define the restriction of $W$ to a region $[i,j]$ to be the subdiagram obtained by forgetting all propagators not wholly supported on vertices in the cyclic interval $[i,j]$; the vertex set remains the same as in $W$.  Denote this diagram by $W_{[i,j]}$.

Note that if $p$ is a propagator supported on $(i,j)$, then we can consider two obvious restrictions of $W$, namely $W_{[i,j+1]}$ and $W_{[j,i+1]}$.  Clearly all other propagators $q\neq p$ appear in exactly one of these subdiagrams, while $p$ appears in both.  In this case, we will say that $p$ \textit{bounds the regions} $[i,j+1]$ and $[j,i+1]$; the ordering of the start and end points allow us to identify one or the other region unambiguously.

With these observations in mind we can return to the proof.

@@

Start by choosing a propagator $p_1$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}), and write $(j_1,j_1+2)$ for its support.  If it is part of one of the configurations we are looking for then we are done, 
%a configuration \eqref{eq:2 prop config} we are done,
so suppose otherwise: since $p_1$ is not in configuration \ref{item lonely 2} then there must be a second propagator starting either on edge $j_1)$ or $j_1+2$.  Flipping the diagram if necessary, assume the former.  Since $p_1$ is not in configuration \ref{item pair of 2s} and every vertex is supported then there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.  This bounds a region $[i_1,k_1]$ (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.

Now suppose $q_{r}$ exists by the induction hypothesis and bounds a region $[i_r,k_r]$ not containing any $p_i$ for $i\leq r$.  Consider the restricted diagram $W_r:=W_{[i_r,k_r]}$; by the original hypotheses on $W$ every vertex $l \in [i_r+2,k_r-2]$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $l \in \{i_r,i_r+1,k_r-1,k_r\}$ because of $q_r$.

By Remark~\ref{rem:props of length 2 and 3}, $W_r$ admits at least one propagator of length 2.  $W_r$ has no propagators of length $3$ since $W$ has none.  Let $p_{r+1}$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item lonely 2}, \ref{item pair of 2s}, or \ref{item 4 and 2}
%the configuration \eqref{eq:2 prop config}
then we are done, so assume otherwise.

Note we may replace $q_r$ by any other propagator of length $\geq 4$ in $W_r$ which contains $p_{r+1}$ and such a new $q_r$ still satisfies all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ which contain $p_{r+1}$.

There are two cases to consider.
The first case is that $p_{r+1}$ has one end before $i_r+3$ and the other after $k_r-3$.  Then since $p_{r+1}$ has length 2, it must be that $[i_r+3,k_r-3]$ is at most a single edge, and so $q_r$ has length $\leq 6$.  The only propagators inside $q_r$ that do not also contain $p_{r+1}$ must have both ends in $[i_r, i_r+3]$ or both ends in $[k_r-3, k_r]$ and hence be of length 2.  Therefore, if $q_r$ contains a propagator $t$ of length $\leq 4$, this propagator must also contain $p_{r+1}$ which is impossible my minimality.  Therefore, if $q_r$ contains another propagator of length $2$ we would have configuration \ref{item pair of 2s} which we have already assumed does not occur.  Consequently, $q_r$ contains only $p_{r+1}$; if $q_r$ is of length $4$ then we have \ref{item 4 and 2} and if $q_r$ is of length $5$ or $6$ then we have either \ref{item lonely 2} or an unsupported vertex, all of which are impossible.  Therefore the first case cannot occur.

The second case is that either at least one endpoint of $p_{r+1}$ lies on an edge contained in the interval $[i_r+3,k_r-3]$, or both ends lie in $[i_r, i_r+3]$ or $[k_r-3, k_r]$; these situations all behave similarly.  Up to symmetry we can write $p_{r+1} = (j_{r+1}, j_{r+1}+2)$ where either the edge $j_{r+1}+2$ is contained in $[i_r+3, k_r-3]$ or $j_{r+1}+2 = i_r+2$.  Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and vertex $j_{r+1}+4$ is supported (and not by $q_r$ since $j_{r+1}+4 \leq k_r-2$ in both situations), there is some propagator $t$ with one end in $[j_{r+1}+3, j_{r+1}+5]$ and length $\geq 4$.  By noncrossingness $t$ is contained in $q_{r}$.  $t$ does not contain $p_{r+1}$ by minimality and so we may set $q_{r+1} = t$ to continue the induction.

>>>>

\begin{lem}\label{lem facts about WLD matroids}
Let $W = (\cP,n)$ be an admissible Wilson loop diagram. Then:
\begin{enumerate}
\item The rank of a set $V \subseteq [n]$ is bounded above by $\min\{|V|,|\Prop(V)|\}$, with $\rk(V) = |V|$ if and only if $V$ is an independent set.
%\item Let $v \in [n]$ and $q \in \Prop(v)$. Then for any $V \subset [n]$ such that $q \not \in \Prop(V)$, we have $\rk(V \cup \{v\}) = \rk(V) +1$, i.e. adding a vertex that supports a new propagator to a set increases the rank of the set.
\item If $C \subseteq [n]$ is a cycle, then $\rk(C) = |Prop(C)|$.
\item If $[n]$ can be partitioned into at least two non-empty sets, each of which support different sets of propagators, \bas [n] = \cup_i V(P_i) \quad \textrm{s.t.} \quad \cup P_i = \cP; \quad  P_i \cap P_j = \emptyset \;, \eas the the matroid $M(W)$ is seperable, \bas M(W) = \bigoplus_i M(P_i, V(P_i)) \;.\eas 
\end{enumerate}
\end{lem}
\begin{proof}
The first part of (1) is \cite[Equation (9)]{wilsonloop} and surrounding discussion, and the second part is standard matroid theory. (2) is \cite[Lemma 3.27]{wilsonloop}. (3) is also in \cite[Lemma FIND]{wilsonloop}.
\end{proof}

@@

\begin{lem} \label{lem decompose flat}Let $F$ be a flat in $M(W)$, and let $C \subseteq F$ be the union of all circuits contained in $F$. Then the following are true:
\begin{enumerate}
\item $C = F(\Prop (C))$, i.e. $C$ is a propagator flat.
\item $F \setminus C$ is an independent  flat.  
\end{enumerate}
\end{lem}

@@

Let $v \in C$. Clearly $\Prop(v) \subseteq \Prop(C)$, and so by Lemma \ref{lem properties of prop flatfs} we have $F(\Prop(v)) \subseteq F(\Prop(C))$. Since $v \in F(\Prop(v))$ by the definition of propagator flat, we have $v \in F(\Prop(C))$ as required.

@@

For part (2), first note that $F \setminus C$ is automatically independent as it contains no circuits.

@@

\begin{lem} \label{maxexactcomplementrank}
Let $W = (\cP, n)$ be a Wilson loop diagram, and $P \subseteq \cP$. Then: \begin{enumerate}
\item If $(P,V(P))$ is an exact subdiagram in $W$, then $\rk(F(P^c)) = |P^c|$.
\item If $(P,V(P))$ is a maximal exact subdiagram in $W$, then $F(P^c)$ is a cyclic flat.
\end{enumerate}
\end{lem}

Note that by definition, since $F(P^c)$ has at $|P^c|$ propagators in it, this is an upper bound on the rank. However, showing equality on the first part is harder.

@@

We address part (2) first. Suppose that $(P, V(P))$ is a maximal exact subdiagram; by Corollary \ref{classifyflats} we can decompose $F(P^c)$ as
\begin{equation}\label{eq decompose F}F(P^c) = C \sqcup S,\end{equation}
where $C$ is the largest cyclic flat contained in $F(P^c)$ and $S$ is an  independent set. Note that $C$ must be non-empty since $F(P^c)$ is dependent. We proceed by showing that $S$ must be empty, forcing $F(P^c)$ to be a cyclic flat.

Since $C = F(\Prop(C))$ by Lemma \ref{lem decompose flat}, define $Q := \Prop(C)^c$ so that we may write $C = F(Q^c) = V(Q)^c$. Note that since $C \subseteq F(P^c)$, $P \subseteq Q$. Furthermore, we have 
\begin{equation}\rk(S) = |S| \leq \rk(F(P^c)) - \rk(C)  \leq |P^c| - \rk(C) \;, \label{increasingrank}\end{equation}
where first equality comes from the fact that $S$ is an independent set, and the final inequality comes from Lemma \ref{lem facts about WLD matroids}(1). Since $\rk(C) = |\Prop(C)| = |Q^c|$ by Lemma \ref{lem facts about WLD matroids}(2), we can rearrange \eqref{increasingrank} to obtain the inequality
\begin{equation} |P| + |S| \leq |P| + |P^c| - \rk(C) = |Q| \;. \label{Qsizebound}\end{equation}
Furthermore, since $V(Q) = S \sqcup V(P)$ (by equation [ref] and the definition of $Q$) we may write  
\begin{equation} |V(Q)| = |S| + |V(P)| = |S| + |P| +3 \label{VQsize} \;.\end{equation} 
Combining this with \eqref{Qsizebound} gives $|V(Q)| - 3 \leq |Q|$. That is, either $W$ was not admissible, or $(P,V(P))$ was not a maximal exact subdiagram. In other words, $S$ cannot be non-empty, proving that $F(P^c)$ is a cyclic flat, and therefore of maximal rank.

Let $P$ be a maximal exact subdiagram as above, and let $(R, V(R))$ be an exact subdiagram that is not maximal. That is, $R \subsetneq P$.

Since $R \subset P$, $V(P) = V(R) \sqcup S$. Since $P$ and $R$ both define exact subdiagrams, we may write $|V(P)| = |V(R)| + |P \setminus R|$, where $S$ is a vertex set of size $|P \setminus R|$ with $(P \setminus R \subset \Prop(S)$. Since $\rk V(P) =  \rk V(R) + |P \setminus R|$, $S$ is independent. Taking the complements, we may write \bas F(R^c ) = F(P^c) \sqcup S \;.\eas Since $S$ is an independent set of vertices of the correct size supporting the appropriate propagators, this gives $ \rk F(R^c ) = |R^c|$.

@@

In \cite{wilsonloops}, the authors show that all violet Wilson loop diagrams correspond to positroids. That is, they correspond to matroids that can be represented by elements of the positive Grassmannians $\Gr(|\cP|, |V|)$. Any positroid of rank $k$ on $n$ elements defines a subspace of the positive Grassmannians $\Gr(k, n)$, namely the points which represent it. These subspaces give a CW structure on $\Gr(k,n)$, with each positroid defining a cell.

\begin{dfn}
Given a Wilson loop diagram $W = (\cP, [n])$, define the positroid cell associated to a Wilson loop diagram, $\Sigma(W)$, to be the cell in the CW complex on $\Gr(|\cP|, n)$ defined by the positroid $M(W)$.
\end{dfn}

@@

\note{I don't think rank of a vertex (in the sense of number of propagators supported on it) was ever used, so I removed the definition}
%\note{rank probably isn't a good word; do we have a better one?}
%\begin{dfn}\label{vertex rank}
%Let $i$ be a vertex in $W$. We define the {\bf rank} of $i$ to be $|Prop(i)|$, i.e. the number of propagators supported on $i$.
%\end{dfn}

@@

\begin{dfn}\note{right now this doesn't depend on the order of $i$ and $j$, but that might matter later on?}
Let $p$ be a propagator supported on the vertices $(i,i+1,j,j+1)$.  Define the \textit{length} of $p$ to be 
\[\ell(p) = min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
\end{dfn}

\begin{rmk}\label{rem:props of length 2 and 3}
The following observations about propagators of short length in $W$ are easily verified:
\begin{itemize}
\item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.
\item If $p = (i,i+1,i+3,i+4)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
\end{itemize}
\end{rmk}

\note{Are the next few definitions used outside the proof of Lemma~\ref{lem sian 1}?  If not, then perhaps they could go inside the proof so as not to clutter the document with temporary definitions?}
\begin{dfn}
Define the restriction of $W$ to a region $[i,j]$ to be the subdiagram obtained by forgetting all propagators not wholly supported on vertices in the cyclic interval $[i,j]$.  Denote this diagram by $W_{[i,j]}$.
\end{dfn}
\note{I think there's an issue here about what we mean by subdiagram; in def 1.5 we say a subdiagram is of the form $(P, V(P))$ which is certainly not what we want here; in fact I think we want the subdiagram where the vertex set is unchanged and only the propagator set is restricted (the other possibility would be to restrict the vertex set to $[i, j]$, but then the lengths of propagators can change and in the way we want to use it (see paragraph below) $p$ will become very non-admissible).  I think def 1.5 should be removed and we should say that for a WLD $(P, V)$ subdiagrams are any $(P', V')$ with $P'\subseteq P$, $V'\subseteq V$ and all supporting vertices of elements of $P'$ in $V'$; this seems to me to be the natural notion of subobject.}

If $p$ is a propagator supported on $(i,i+1,j,j+1)$, then we can consider two obvious restrictions of $D$, namely $D_{[i,j+1]}$ and $D_{[j,i+1]}$.  Clearly all other propagators $q\neq p$ appear in exactly one of these subdiagrams, while $p$ appears in both.  In this case, we will say that $p$ \textit{bounds the regions} $[i,j+1]$ and $[j,i+1]$; the ordering of the start and end points allow us to identify one or the other region unambiguously.

@@

\begin{lem}\label{lem sian 1}
  Let $W$ be an admissible WLD in which each vertex supports at least one propagator.  Then exactly one of the following two things occurs.
  \begin{enumerate}
    \item $W$ has a propagator of length 3 with a propagator of length 2 inside it.
    \item $W$ admits no propagators of length 3, and one or more of the following things occurs.
      \begin{enumerate}
        \item There is a propagator of length $2$, say $(i, i+1, i+2, i+3)$ such that no other propagators ends on either the edge $(i, i+1)$ or the edge $(i+2, i+3)$.\label{item lonely 2}
        \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+1, i+2, i+3)$, the second is $(j, j+1, j+2, j+3)$, no other propagator ends between $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
        \item There exists a propagator of length exactly 4 with only a propagator of length 2 inside it.\label{item 4 and 2}
      \end{enumerate}
  \end{enumerate}
\end{lem}

\begin{proof}
  Suppose first that $W$ has a propagator of length $3$, $p=(i, i+1, i+3, i+4)$.  By Remark~\ref{rem:props of length 2 and 3} along with the fact that every vertex of $W$ supports at least one propagator, we have that $i+2$ supports exactly one propagator and this propagator must have length 2 by noncrossingness.

@@

@@

Start by choosing a propagator $p_1$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}), and write $(j_1,j_1+1,j_1+2,j_1+3)$ for its support.  If it is part of one of the configurations we are looking for then we are done, 
%a configuration \eqref{eq:2 prop config} we are done,
so suppose otherwise: since $p_1$ is not in configuration \ref{item lonely 2} then there must be a second propagator starting either on edge $(j_1, j_1+1)$ or $(j_1+2, j_1+3)$.  Flipping the diagram if necessary, assume the former.  Since $p_1$ is not in configuration \ref{item pair of 2s} and every vertex is supported then there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $(j_1,j_1+1)$ or on edge $(j_1-1, j_1)$ or on edge $(j_1-2, j_1-1)$.  This bounds a region $[i_1,k_1]$ (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.

Now suppose $q_{r}$ exists by the induction hypothesis and bounds a region $[i_r,k_r]$.  Consider the restricted diagram $W_r:=W_{[i_r,k_r]}$; by the original hypotheses on $W$ every vertex $l \in [i_r+2,k_r-2]$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $l \in \{i_r,i_r+1,k_r-1,k_r\}$ because of $q_r$.

By Remark~\ref{rem:props of length 2 and 3}, $W_r$ admits at least one propagator of length 2.  $W_r$ has no propagators of length $3$ since $W$ has none. \note{now the question really is important about what length means in the restricted diagram; as written the restricted diagram has the same vertex set so length is unchanged.}   Let $p_{r+1}$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item lonely 2}, \ref{item pair of 2s}, or \ref{item 4 and 2}
%the configuration \eqref{eq:2 prop config}
then we are done, so assume otherwise.

Note we may replace $q_r$ by any other propagator of length $\geq 4$ in $W_r$ which contains $p_{r+1}$ while still satisfying all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ which contain $p_{r+1}$.

There are two cases to consider.
The first case is that neither end of $p_{r+1}$ lies on an edge contained in the possibly empty interval $[i_r+3,k_r-3]$, then since $p_{r+1}$ has length 2, it must be that $[i_r+3,k_r-3]$ is at most a single edge, and so $q_r$ has length $\leq 6$.  Since $p_{r+1}$ has one end before $i_r+3$ and the other after $k_r-3$, the only propagators inside $q_r$ that do not also contain $p_{r+1}$ must have both ends in $[i_r, i_r+3]$ or both ends in $[k_r-3, k_r]$ and hence be of length 2.  Therefore, if $q_r$ contains a propagator $t$ of length $\leq 4$, this propagator must also contain $p_{r+1}$ which is impossible my minimality.  Therefore, if $q_r$ contains another propagator of length $2$ we would have configuration \ref{item pair of 2s} which we have already assumed does not occur.  Consequently, $q_r$ contains only $p_{r+1}$; if $q_r$ is of length $4$ then we have \ref{item 4 and 2} and if $q_r$ is of length $5$ or $6$ then we have either \ref{item lonely 2} or an unsupported vertex, all of which are impossible.  Therefore the first case cannot occur.

The second case is that at least one endpoint of $p_{r+1}$ lies on an edge contained in the interval $[i_r+3,k_r-3]$.  Up to symmetry we can write $p_{r+1} = (j_{r+1}, j_{r+1}+1, j_{r+1}+2, j_{r+1}+3)$ where $(j_{r+1}+2, j_{r+1}+3)$ is contained in $[i_r+3, k_r-3]$.  Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and vertex $j_{r+1}+4$ is supported (and not by $q_r$ since $j_{r+1}+4 \leq k_r-2$), there is some propagator $t$ with one end in $[j_{r+1}+2, j_{r+1}+4]$ and length $\geq 4$.  By noncrossingness $t$ is contained in $q_{r}$.  $t$ does not contain $p_{r+1}$ by minimality and so we may set $q_{r+1} = t$ to continue the induction.
